Visual diagnostics for constrained optimisation with application to guided tours

### 2020-10-07 paper/paper.Rmd
fixing on section 5 examples

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their initial paper on projection pursuit in 1974 that "the  technique  used  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied more generally to help practitioner to unveil the black-box in randomised iterative (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm, array}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::asa_article
editor_options: 
  chunk_output_type: console
---

@@

\newpage

@@

```{r tour-path, out.width="100%", out.height="60%", fig.cap="\\label{tour-path}An illustration of the tour path"}
knitr::include_graphics(path = here::here("figures/tour_path_keynote/tour_path_keynote.001.png"))
```

@@

```{r toy-interp, fig.height = 8, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
p1 <- holes_2d_better_max_tries %>% explore_trace_interp() + theme(legend.position = "none") + 
  scale_color_botanical(palette = "fern")

@@

\newpage

@@

```{r toy-pca, fig.height = 6, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
# path1 <- holes_1d_geo$basis %>% 
#   flatten_dbl() %>% 
#   matrix(ncol = 5, byrow = TRUE)
# path2 <- holes_1d_better$basis %>% 
#   flatten_dbl() %>% 
#   matrix(ncol = 5, byrow = TRUE)
# set.seed(1)
# sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
# theoretical <- matrix(c(0, 1, 0, 0, 0,
#                         0, -1, 0, 0, 0), nrow = 2, byrow = TRUE)
# 
# dt <- rbind(sphere, path1, path2, theoretical)
# pca <- dt %>% prcomp(scale. = TRUE)
# #summary(pca)
# pca_pred <- predict(pca) %>%
#   as_tibble() %>%
#   mutate(method = c(rep("sphere", nrow(sphere)),
#                     holes_1d_geo$method,
#                     holes_1d_better$method,
#                     rep("theoretical", 2))) %>%
#   group_by(method) %>%
#   mutate(id = row_number(),
#          id = ifelse(method == "sphere", 1, id)) %>%
#   ungroup()
# 
# p <- pca_pred %>%
#   ggplot(aes(x = PC1, y = PC2, color = method))+
#   geom_point() +
#   geom_point(data = pca_pred %>% filter(method == "theoretical"), 
#              size = 10) + 
#   geom_point(data = pca_pred %>% filter(method %in% c("search_better", "search_geodesic") & id == 1), size = 10) + 
#   theme(aspect.ratio = 1) + 
#   scale_color_botanical(palette = "cherry")
# 
# p

@@

For a particular index function, the best algorithm to optimise is related to the character of the index and the data. If the index function is smooth and has single maximum, all of the three algorithms introduced above can find maximum.  When multiple optima are presented, `search_better` may stuck in the local maximum. When the index function is non-smooth, `search_geodesic` may even fail to find the maximum. In this section, examples will be presented  to outline how the diagnostic plots can be used to compare the performance of the algorithms in different scenarios.

@@

Random variables with different structures has been simulated and the distribution of each is presented in Equation \ref{eq:sim-norm} to \ref{eq:sim-x7}. Variable `x1`, `x8`, `x9` and `x10` are normal distributed with zero mean and unit variance and `x2` to `x7` are mixture of normal distributions with different weights and locations. Figure \ref{origin-data} plots the histogram of each variable except `x3`. The mixture variables are scaled to have unit variance before running the projection pursuit.

@@

```{r origin-data, fig.cap="\\label{origin-data} The histogram of simulated selected variables."}
origin_dt_bi <- data_mult %>% 
  dplyr::select(-c(x3, x8, x9, x10)) %>% 
  gather(names, values) %>%
  mutate(names = as_factor(names))

origin_dt_bi %>%
  ggplot(aes(x = values)) +
  geom_histogram(binwidth = 0.3) +
  geom_density(aes(y = 0.3 * ..count..)) +
  facet_wrap(vars(names), ncol = 3)
```

@@

```{r interpolation}
#points is always included in the newest version
# p1 <- holes_2d_better %>%
#   filter(info == "interpolation") %>%
#   ggplot(aes(x = tries, y = index_val, col = as.factor(tries))) +
#   geom_point() +
#   geom_line(aes(group = 1))
# 
# p2 <- holes_2d_better %>% explore_trace_interp() + geom_point(aes(col = as.factor(tries)))
# 
# (p1 | p2)  &
#   theme(legend.position = "bottom")
# 
```

@@

p1 | p2
#xxx up and down plot allows for displaying time series features while left and right display makes it easier for comparison? The same problem for plot of comparing between different searching methods
```

@@

```{r sample-code, eval = FALSE, echo = TRUE}
set.seed(123456)
holes_2d_geo <- animate_xy(data_mult[,c(1,2, 7:10)],tour_path = 
                             guided_tour(holes(), d = 2, 
                                         search_f = tourr:::search_geodesic),
                           rescale = FALSE, verbose = TRUE)

last_basis <- holes_2d_geo %>% filter(info == "interpolation") %>% 
  tail(1) %>% pull(basis) %>% .[[1]]

set.seed(123456)
holes_2d_geo_polish <- animate_xy(data_mult[,c(1,2, 7:10)], tour_path = 
                                    guided_tour(holes(), d = 2, 
                                                search_f = tourr:::search_polish),
                                  rescale = FALSE, verbose = TRUE, 
                                  start = last_basis)
```

A slight variation of the plot definition due to the addition of polishing points is as follows:

- Layer 1: point geom
  - data: filter the observations with  $S = \text{interpolation}$; bind the data object from optimisation and interpolation and form polishing; mutate $t$ to be the row number of the binded tibble.
  - x: $t$ is mapped to the x-axis
  - y: $I$ is mapped to the y-axis 
  - colour: $V$ is mapped to the colour aesthetic

- Layer 2: line geom

<!-- Polishing points form on itself a global structure with candidate bases and output bases. If we're allowed to abuse the notation a bit, we denote $$A_{J, \ast, \sum_{i = 1}^J k_i + 1}$$ as the first polishing basis and $$A_{J, \ast, \sum_{i = 1}^J k_i + M}$$ as the last polishing basis, where $$M = \sum_i S_{i, \text{method}} \mathds{1}(\text{method} = \text{polish})$$ -->

<!-- Then the index plot incorporating both the interpolating points and polishing points can be defined as  -->

<!-- $$x = \{1, 2, \cdots, \sum_{i = 1}^J k_i,(\sum_{i = 1}^J k_i + 1), \cdots,  \sum_{i = 1}^J k_i + M\}$$ -->
<!-- $$y = \{I_{jlk}: k = x\}$$ -->

---

Again using the same data, we are interested to compare the effect of different `max.tries` in the 2D projection setting. `max.tries` is a hyperparameter that controls the maximum number of try before the search ends. The default value of 25 is suitable for 1D projection while we suspect it may not be a good option for the 2D case and hence want to compare it with an alternative, 500. As shown in Figure \ref{trace-compare}, both trials attain the same index value after polishing while the small `max.tries` of 25 is not sufficient for `search_better` to find its global maximum and we will need to adjust the `max.tries` argument for the search to sufficiently explore the parameter space.

```{r polish, fig.asp=0.5,fig.cap="\\label{trace-compare}Breakdown of index value when using different max.tries in search better in conjunction with search polish. Both attain the same final index value after the polishing while using a `max.tries` of 25 is not sufficient to find the true maximum."}

holes_2d_better %>% mutate(max_tries = 25) %>% 
  dplyr::bind_rows(holes_2d_better_max_tries %>% mutate(max_tries = 500)) %>% 
  explore_trace_interp(col = max_tries) + 
  theme(legend.position = "none")
```

@@

[add example from geozoo]

@@

```{r kol-cdf,fig.asp=0.5, fig.cap = "\\label{kol-cdf}Comparison of two different searching methods: search_geodesic and search_better on 1D projection problem for a noisier index: kol_cdf. The geodesic search rely heavily on the polishing step to find the final index value while search better works well."}
# p1 <- bind_rows(kol_1d_geo, kol_1d_geodesic_polish) %>% explore_trace_interp(col = method)  + ggtitle("search_geodesic")
# 
# p2 <- bind_rows(kol_1d_better, kol_1d_better_polish) %>% explore_trace_interp(col = method) + ggtitle("search_better")
# 
# (p1 | p2 ) & theme(legend.position = "bottom") & ylim(0, 0.23)

p1 <- kol_1d_geo %>% explore_trace_interp(col = method)  + ggtitle("search_geodesic")

p2 <- kol_1d_better %>% explore_trace_interp(col = method) + ggtitle("search_better")

(p1 | p2 ) & theme(legend.position = "bottom") & ylim(0, 0.23)
```

@@

Using different seeds in `search_better` allows us to find both local maxima d as in Figure \ref{1d-2var-different-seeds}. Comparing the maximum of both, we can see that the global maximum happens when `x2` is found. It is natural to ask then if there is an algorithm that can find the global maximum without trying on different seeds? `search_better_random` manages to do it via a Metropolis-hasting random search as shown in Figure \ref{1d-2var-better-random}, although at a higher cost of number of points to evaluate.

```{r 1d-2var-different-seeds,  fig.asp=0.5, fig.cap="\\label{1d-2var-different-seeds}The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum."}
colour <- ferrn::botanical_pal()(3)
p5 <- kol_1d_2var_better %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[2]) + ggtitle("search_better, seed 123456")
p6 <- kol_1d_2var_better_2 %>% explore_trace_interp(col = 0) + 
  scale_colour_manual(values = colour[1]) + ggtitle("search_better, seed 12345")

(p5 | p6) & theme(legend.position = "none") & ylim(0, 0.25)
```

```{r 1d-2var-better-random, fig.asp=0.5, fig.cap = "\\label{1d-2var-better-random}Using search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed."}
kol_1d_2var_better_random %>% 
  explore_trace_interp(col = 0) + 
  ylim(0, 0.25) + 
  scale_colour_manual(values = colour[3]) + 
  theme(legend.position = "none") + 
  ggtitle("search_better_random")
```

We can also plot the searching points of all three algorithms in the searching space and explore their relative position against each other using principal components. As shown in Figure \ref{1d-2var-explore-proj-pca}, the bases from better1 and better2 only search a proportion of the searching space while better_random produces a more exhaustive search. The large overlapping of better1 and better_random is explained by the fact that both algorithms find x2 in the end.

<!-- ```{r 1d-2var-explore-proj-pca, fig.cap = "\\label{1d-2var-explore-proj-pca} The projected projection basis using principal components. The bases from better1 and better2 only search a proportion of the searching space while better_random produces a more exhausive search. The large overlapping of better1 and better_random is explained by the fact that both algorithms finds x2 in the end."} -->
<!-- interp1 <- kol_cdf_1d_2var_better  -->
<!-- interp2 <- kol_cdf_1d_2var_better_2 -->
<!-- interp3 <- kol_cdf_1d_2var_better_random  -->

<!-- dt <- bind_rows(interp1, interp2, interp3) %>%  -->
<!--   mutate(algorithm = c(rep("better 1", nrow(interp1)),  -->
<!--                        rep("better 2", nrow(interp2)),  -->
<!--                        rep("better random", nrow(interp3))), -->
<!--          algorithm = fct_relevel(algorithm, c("better 1", "better 2", "better random")))  -->

<!-- dt %>%  -->
<!--   explore_proj_pca(col = algorithm, alpha = 0.5) +  -->
<!--   scale_colour_manual(values = color(3))  -->
<!-- ``` -->

>>>>

- name: Author 1
  thanks: The authors gratefully acknowledge ...
  affiliation: Department of YYY, University of XXX
- name: Author 2
  affiliation: Department of ZZZ, University of WWW
keywords:
- optimisation
- projection pursuit 
- guided tourr
- visual 
- diagnostics 
- R
abstract: Friedman & Tukey commented on their initial paper on projection pursuit in 1974 that "the  technique  used  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." While many projection pursuit indices have been proposed in the literature, few concerns the optimisation procedure. In this paper, we developed a system of diagnostics aiming to visually learn how the optimisation procedures find its way towards the optimum. This diagnostic system can be applied more generally to help practitioner to unveil the black-box in randomised iterative (optimisation) algorithms. An R package, ferrn, has been created to implement this diagnostic system.
bibliography: biblio.bib
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm, array}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 4
editor_options: 
  chunk_output_type: console
---

@@

@@

```{r tour-path, out.width="60%", out.height="40%", fig.align='center', fig.cap="\\label{tour-path}An illustration of the tour path"}
knitr::include_graphics(path = here::here("figures/tour_path_keynote/tour_path_keynote.001.png"),)
```

@@

```{r toy-interp, fig.cap = "\\label{toy-interp} This is a toy example of plotting interpolated points"}
p1 <- holes_2d_better_max_tries %>% explore_trace_interp() + theme(legend.position = "none") + 
  scale_color_botanical(palette = "fern")

@@

\

@@

```{r toy-pca, fig.height = 4, fig.cap = "\\label{toy-pca}PCA plot of search geodesic colouring by info allows for better understanding of each stage in the geodesic search"}
# path1 <- holes_1d_geo$basis %>% 
#   flatten_dbl() %>% 
#   matrix(ncol = 5, byrow = TRUE)
# path2 <- holes_1d_better$basis %>% 
#   flatten_dbl() %>% 
#   matrix(ncol = 5, byrow = TRUE)
# set.seed(1)
# sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
# theoretical <- matrix(c(0, 1, 0, 0, 0,
#                         0, -1, 0, 0, 0), nrow = 2, byrow = TRUE)
# 
# dt <- rbind(sphere, path1, path2, theoretical)
# pca <- dt %>% prcomp(scale. = TRUE)
# #summary(pca)
# pca_pred <- predict(pca) %>%
#   as_tibble() %>%
#   mutate(method = c(rep("sphere", nrow(sphere)),
#                     holes_1d_geo$method,
#                     holes_1d_better$method,
#                     rep("theoretical", 2))) %>%
#   group_by(method) %>%
#   mutate(id = row_number(),
#          id = ifelse(method == "sphere", 1, id)) %>%
#   ungroup()
# 
# p <- pca_pred %>%
#   ggplot(aes(x = PC1, y = PC2, color = method))+
#   geom_point() +
#   geom_point(data = pca_pred %>% filter(method == "theoretical"), 
#              size = 10) + 
#   geom_point(data = pca_pred %>% filter(method %in% c("search_better", "search_geodesic") & id == 1), size = 10) + 
#   theme(aspect.ratio = 1) + 
#   scale_color_botanical(palette = "cherry")
# 
# p

@@

For a particular index function, the best algorithm to optimise relates to the character of the index and the data. If the index function is smooth and has single maximum, all of the three algorithms introduced above can find the maximum.  When multiple optima are presented, `search_better` may stuck in the local maximum and in the case where the index function is non-smooth, `search_geodesic` may even fail to find the maximum. In this section, examples will be presented  to outline how the diagnostic plots can be used to compare the performance of the algorithms in different scenarios.

@@

Random variables with different structures has been simulated and the distribution of each is presented in Equation \ref{eq:sim-norm} to \ref{eq:sim-x7}. Variable `x1`, `x8`, `x9` and `x10` are normal distributed with zero mean and unit variance and `x2` to `x7` are mixtures of normal distributions with varied weights and locations. The mixture variables have been scaled to have an overall unit variance before running the projection pursuit.

@@

@@

@@

p1 | p2

@@

```{r sample-code, eval = FALSE, echo = TRUE}
library(tourr)
library(ferrn)

set.seed(123456)
holes_2d_geo <- 
  animate_xy(boa6,
             tour_path = guided_tour(holes(), d = 2, 
                                     search_f = search_geodesic),
             rescale = FALSE, verbose = TRUE)

last_basis <- get_best(holes_2d_geo) %>% pull(basis) %>% .[[1]]

set.seed(123456)
holes_2d_geo_polish <- 
  animate_xy(boa6, 
             tour_path = guided_tour(holes(), d = 2, 
                                     search_f = search_polish),
             rescale = FALSE, verbose = TRUE, start = last_basis)
```

Checking the final projection before and after applying the polish as in Figure \ref{geo-polish}, we can see that ...

```{r geo-polish, fig.height= 2.5, fig.cap = "\\label{geo-polish}On the left is the final projection from search geodesic while on the right is the polished result. Polishing helps to sharpen the edges of the clusters"}
# set.seed(123456)
# render(
#   boa6,
#   tour_path = guided_tour(holes(), d = 2, search_f = search_geodesic),
#   dev = "png",
#   display = display_xy(axes = "bottomleft", verbose = TRUE),
#   rescale = FALSE,
#   frames = 100,
#   file = here::here("figures","geo_polish", "before%03d.png")
# )
# 
# last_basis <- get_best(holes_2d_geo)$basis %>% .[[1]]
# 
# set.seed(123456)
# render(
#   boa6,
#   tour_path =  guided_tour(holes(), d = 2, search_f = search_polish, alpha = 0.1),
#   dev = "png",
#   display = display_xy(axes = "bottomleft", verbose = TRUE),
#   start = last_basis,
#   rescale = FALSE,
#   frames = 100,
#   file = here::here("figures","geo_polish", "after%03d.png")
# )

before <- png::readPNG(here::here("figures","geo_polish", "before100.png"))
after <- png::readPNG(here::here("figures","geo_polish", "after004.png"))
gl <-  lapply(list(before, after), grid::rasterGrob)
wrap_plots(gl) 
```

<!-- --- -->

<!-- Again using the same data, we are interested to compare the effect of different `max.tries` in the 2D projection setting. `max.tries` is a hyperparameter that controls the maximum number of try before the search ends. The default value of 25 is suitable for 1D projection while we suspect it may not be a good option for the 2D case and hence want to compare it with an alternative, 500. As shown in Figure \ref{trace-compare}, both trials attain the same index value after polishing while the small `max.tries` of 25 is not sufficient for `search_better` to find its global maximum and we will need to adjust the `max.tries` argument for the search to sufficiently explore the parameter space. -->

<!-- ```{r polish, fig.asp=0.5,fig.cap="\\label{trace-compare}Breakdown of index value when using different max.tries in search better in conjunction with search polish. Both attain the same final index value after the polishing while using a `max.tries` of 25 is not sufficient to find the true maximum."} -->

<!-- holes_2d_better %>% mutate(max_tries = 25) %>%  -->
<!--   dplyr::bind_rows(holes_2d_better_max_tries %>% mutate(max_tries = 500)) %>%  -->
<!--   explore_trace_interp(col = max_tries) +  -->
<!--   theme(legend.position = "none") -->
<!-- ``` -->

@@

@@

```{r kol-cdf,fig.asp=0.5, fig.cap = "\\label{kol-cdf}Comparison of two different searching methods: search_geodesic and search_better on 1D projection problem for a noisier index: kol_cdf. The geodesic search rely heavily on the polishing step to find the final index value while search better works well."}
# set.seed(123456)
# kol_1d_geo <- 
#   animate_dist(boa5, tour_path = guided_tour(norm_kol(), d = 1,
#                                              search_f =  search_geodesic, max.tries = 100),
#                rescale = FALSE, verbose = TRUE)
# 
# set.seed(123456)
# kol_1d_better <- 
#   animate_dist(boa5, tour_path = guided_tour(norm_kol(), d = 1,
#                                              search_f =  search_better, max.tries = 100),
#                rescale = FALSE, verbose = TRUE)
# save(kol_1d_geo, file = here::here("data", "kol_1d_geo.rda"))
# save(kol_1d_better, file = here::here("data", "kol_1d_better.rda"))

bind_rows(kol_1d_geo, kol_1d_better) %>% 
  explore_trace_interp(col = method, group = method) +
  facet_wrap(vars(method), ncol = 2) + 
  scale_color_botanical() +
  theme(legend.position = "none", aspect.ratio = 1)

@@

Using different seeds in `search_better` allows us to find both local maxima d as in Figure \ref{1d-2var-different-seeds}. Comparing the maximum of both, we can see that the global maximum happens when `x2` is found. It is natural to ask then if there is an algorithm that can find the global maximum without trying on different seeds? `search_better_random` manages to do it via a Metropolis-hasting random search as shown in Figure \ref{1d-2var-better-random}, although at a higher cost of number of points to evaluate. In Figure \ref{kol-pca}, 
sing search better random for the problem above will result in finding the global maximum but much larger number of iteration is needed. We can also plot the searching points of all three algorithms in the searching space and explore their relative position against each other using principal components. As shown in Figure \ref{1d-2var-explore-proj-pca}, the bases from better1 and better2 only search a proportion of the searching space while better_random produces a more exhaustive search. The large overlapping of better1 and better_random is explained by the fact that both algorithms find x2 in the end. 
The trace plot search better in a 1D projection problem with two informative variables using different seeds (without polishing). Since there are two informative variables, setting different value for seed will lead search better to find either of the local maximum.

```{r kol-pca, fig.cap = "\\label{kol-pca}THis is the caption"}

# set.seed(123456)
# kol_1d_2var_better <- 
#   animate_dist(boa6, 
#                tour_path = guided_tour(norm_kol(), d = 1,
#                                        search_f = search_better, max.tries = 100),
#                rescale = FALSE, verbose = TRUE)
# 
# 
# set.seed(1234567)
# kol_1d_2var_better_2 <- 
#   animate_dist(boa6, 
#                tour_path = guided_tour(norm_kol(), d = 1,
#                                        search_f = search_better, max.tries = 100),
#                rescale = FALSE, verbose = TRUE)
# 
# set.seed(12345678)
# kol_1d_2var_better_2 <- 
#   animate_dist(boa6, 
#                tour_path = guided_tour(norm_kol(), d = 1,
#                                        search_f = search_better, max.tries = 100),
#                rescale = FALSE, verbose = TRUE)
# 
# 
# 
# 
# set.seed(123456)
# kol_1d_2var_better_random <- 
#   animate_dist(boa6, 
#                tour_path = guided_tour(norm_kol(), d = 1,
#                                        search_f = search_better_random,
#                                        max.tries = 2000, t0 = 1e-5),
#                rescale = FALSE, verbose = TRUE)
# 
# save(kol_1d_2var_better, file = here::here("data", "kol_1d_2var_better.rda"))
# save(kol_1d_2var_better_2, file = here::here("data", "kol_1d_2var_better_2.rda"))
# save(kol_1d_2var_better_random, file = here::here("data", "kol_1d_2var_better_random.rda"))

p1 <- bind_rows(kol_1d_2var_better %>% mutate(algo = "better 1"),
          kol_1d_2var_better_2 %>% mutate(algo = "better 2"),
          kol_1d_2var_better_random %>% mutate(algo = "better random")) %>% 
  explore_trace_interp(group = algo, col = algo) + 
  facet_wrap(vars(algo), ncol = 3)  + 
  scale_color_botanical(palette = "banksia")  + 
  theme(legend.position = "none", aspect.ratio = 1)

pca <- bind_rows(kol_1d_2var_better %>% mutate(algo = "better 1"),
          kol_1d_2var_better_2 %>% mutate(algo = "better 2"),
          kol_1d_2var_better_random %>% mutate(algo = "better random")) %>% 
  bind_theoretical(matrix = matrix(c(0, 1, 0, 0, 0, 0), nrow = 6),
                                        index = tourr::norm_kol(),
                                        raw_data = boa6) %>% 
   bind_theoretical(matrix = matrix(c(0, 0, 1, 0, 0, 0), nrow = 6),
                                        index = tourr::norm_kol(),
                                        raw_data = boa6) %>% 
  compute_pca()

random <- pca$aug %>% filter(method == "randomly_generated") %>% select(-algo)
theoretical <- pca$aug %>% filter(info == "theoretical") %>% select(-algo)

p2 <- pca$aug %>% filter(method != "randomly_generated" & info != "theoretical") %>% 
  ggplot(aes(x = PC1, y = PC2, col = algo)) + 
  geom_point(data = random, col = "grey") +
  geom_point(aes(col = algo), alpha = 0.1) + 
  geom_point(data = theoretical, size = 5, col = botanical_palettes$cherry[3]) + 
  geom_path(data = pca$aug %>% filter(info == "interpolation"), size = 2) + 
  geom_point(data = pca$aug %>% get_best(group = algo), size = 5) +
  geom_point(data = pca$aug %>% get_start(),  size = 5) +
  facet_wrap(vars(algo)) +
  theme_void() + 
  theme(legend.position = "none", aspect.ratio = 1) + 
  scale_color_botanical(palette = "banksia")

wrap_plots(p1, p2, ncol = 1)
